A large-scale analysis of racial disparities in police stops across the United

### 2020-01-21 lib/paper_results.Rmd
Add VOD CIs

```{r veil_of_darkness-appendix_mods}
vod$dst %>%
  select(-data, -base_controls) %>%
  arrange(agency_control, interact_time_loc, spline_degree) %>% 
  select(agency, is_dark, std_error, p_value, everything()) %>%
  kable()
```

>>>>

```{r veil_of_darkness-appendix_mods}
vod$dst %>%
  select(-data, -base_controls) %>%
  mutate(
    l_ci = is_dark - 1.96 * std_error,
    u_ci = is_dark + 1.96 * std_error
  ) %>% 
  arrange(agency_control, interact_time_loc, spline_degree) %>% 
  select(agency, is_dark, std_error, l_ci, u_ci, p_value, everything()) %>%
  kable()
```
